True versus apparent shapes of bow shocks and bow waves

### 2017-11-08 papers/Paper1/sec-thin-shell.tex
Re-write derivation of planitude for ancantoids
Note that C_{k\beta} is now 2 x what it was before

More physically realistic examples of bow shapes are provided by
steady-state hydrodynamic models for the interaction of hypersonic
flows in the thin-shell limit.  The classic examples are the solutions
for the wind--parallel stream and wind--wind problems (see
\S~\ref{sec:intro}) of \citet[][hereafter \CRW{}]{Canto:1996}, where
it is assumed that the two shocks are highly radiative and that the
post-shock flows are perfectly mixed to form a single shell of
negligible thickness. In this approximation, the shape of the shell is
found algebraically by \CRW{} from conservation of linear and angular
momentum, following an approach first outlined in
\citet{Wilkin:1996a}.  For the wind--stream case, the resulting bow
shape was dubbed \textit{wilkinoid} by \citet{Cox:2012a} and has the
form:
\begin{equation}
  \label{eq:wilkinoid-R-theta}
  R(\theta) = R_0\csc\theta\left( 3(1-\theta\cot\theta) \right)^{1/2} \ .
\end{equation}
For the wind--wind case, a family of solutions are found, depending on
the value of \(\beta\), the wind momentum ratio, see
Figure~\ref{fig:crw-schema}, equations~(\ref{eq:stagnation-radius},
\ref{eq:beta-definition}), and surrounding discussion in
\S~\ref{sec:intro}.  We propose that these shapes be called
\textit{cantoids}.  The exact solution for the cantoid shapes
(eqs.~[23, 24] of \CRW{}) is only obtainable in implicit form, but an
approximate explicit solution (eq.~[26] of \CRW{}) is very accurate
for \(\beta \le 0.1\).  The wilkinoid shape corresponds to the
\(\beta \to 0\) limit of the cantoids.  Note that \CRW{}'s \(z\) and
\(r\) axes, which we use in our Figure~\ref{fig:crw-schema},
correspond respectively to the \(x\) and \(y\) axes in
sections~\ref{sec:projection} and \ref{sec:conic} of the current
paper.  By always placing the weaker of the two winds at the origin,
it is only necessary to consider \(\beta \le 1\).

>>>>

More physically realistic examples of bow shapes are provided by
steady-state hydrodynamic models for the interaction of hypersonic
flows in the thin-shell limit.  The classic examples are the solutions
for the wind--parallel stream and wind--wind problems (see
\S~\ref{sec:intro}) of \citet[][hereafter \CRW{}]{Canto:1996}, where
it is assumed that the two shocks are highly radiative and that the
post-shock flows are perfectly mixed to form a single shell of
negligible thickness. In this approximation, the shape of the shell is
found algebraically by \CRW{} from conservation of linear and angular
momentum, following an approach first outlined in
\citet{Wilkin:1996a}.  For the wind--stream case, the resulting bow
shape was dubbed \textit{wilkinoid} by \citet{Cox:2012a} and has the
form:
\begin{equation}
  \label{eq:wilkinoid-R-theta}
  R(\theta) = R_0\csc\theta\left( 3(1-\theta\cot\theta) \right)^{1/2} \ .
\end{equation}

For the wind--wind case, a family of solutions are found that depend on
the value of \(\beta\), the wind momentum ratio, see
Figure~\ref{fig:crw-schema}, equations~(\ref{eq:stagnation-radius},
\ref{eq:beta-definition}), and surrounding discussion in
\S~\ref{sec:intro}.  We propose that these shapes be called
\textit{cantoids}.  The exact solution for the cantoid shapes
(eqs.~[23, 24] of \CRW{}) is only obtainable in implicit form, but an
approximate explicit solution (eq.~[26] of \CRW{}) is very accurate
for \(\beta \le 0.1\).  The wilkinoid shape corresponds to the
\(\beta \to 0\) limit of the cantoids.  Note that \CRW{}'s \(z\) and
\(r\) axes, which we use in our Figure~\ref{fig:crw-schema},
correspond respectively to the \(x\) and \(y\) axes in
sections~\ref{sec:projection} and \ref{sec:conic} of the current
paper.  By always placing the weaker of the two winds at the origin,
it is only necessary to consider \(\beta \le 1\).

A generalization of the cantoids to the case of an
anisotropic\footnote{Note that the wind anisotropy axis must be
  aligned with the star--star axis to maintain cylindrical symmetry.}
inner wind is developed in Appendix~\ref{app:ancantoid}, giving rise
to what we call \textit{ancantoids}, which depend on an anisotropy
index, \(k\), in addition to \(\beta\).
